Leveraging Diversity to Find Bugs in JavaScript Engines

### 2019-02-21 paper/paper.tex
pass on diff
pass on intro

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.
\emph{Related Ideas.}~The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
to prior work on test set diversity, this paper explores diversity of
sources of test cases and diversity of implementations with the goal
of finding bugs. Section~\ref{sec:related-work} elaborates related
work on this topic. Differential Testing~\cite{Brumley-etal-ss07} (DT)
has been applied in a variety of contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of
a given build of their \smonkey\ engine (\eg{}, trying to enable or
not eager JIT compilation\footnote{These files are created with
  the grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach is that
it can be fully automated---as only one engine is used, the outcomes
of the test in both configurations are expected to be identical. The
Mozilla team uses this approach since 2002; they have been able to
find over 270 bugs since then~\cite{jsfunfuzz-at-mozilla}, including
security bugs. Cross-engine differential testing, in contrast, has not
been widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of the techniques aforementioned in finding
bugs on \javascript\ engines.

@@

\emph{Results.}~We considered the following engines--Apple, Google,
Microsoft, and Mozilla. Figure~\ref{fig:summary} shows the breakdown
of bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}). Additionally, each stacked bar breaks
down the bugs per status (\eg{}, ``1-New''). The prefix number
indicates the ordering that status labels are assigned. Note that
several of these reports have the label ``3-Fixed'', indicating that
bug fixes have been incorporated into the code already. Note that most
of these bugs affected two engines--Microsoft's \chakra{} and Apple's
JavaScriptCore (\jsc{}).  We reported \noBugsBugsReportedGoogle{} bugs in Google
\veight{} (\noBugsBugsConfirmedGoogle{} confirmed) and none in
Mozilla's \smonkey{}.  Furthermore, our results show that both
techniques revealed several bugs, most of which confirmed by
developers. Test transplantation revealed \noBugsTransplantation{}
bugs (of which, \noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Considering cost per bug found, we found that test
transplantation, compared to differential testing, demanded less
effort from the developers who inspected the alarms. Most bugs
we found are of moderate severity.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:false-positives}Distribution of False (FP)
    and True Positives (TP).}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9 
    & Timeout/OME & 30 & 15 \\ % 28 & 13
    & * Invalid Input & 46 & 55 \\ % 39 & 48
    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 34 & 28\\ % 34 & 28
    & Bug & 12 & 6\\
    \bottomrule     
  \end{tabular}
\end{table}

@@

\subsection{Diversity in Testing}
The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
assumption behind test set diversity is that faults often spread
contiguously in the input domain. Consequently, it should be
beneficial to partition the input domain and explore it more evenly as
to find bugs faster. Later in the nineties, Chen and
Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
the continuity assumption. They found that faults, most often, manifest
themselves in regular patterns across the input
domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
observations led researchers to investigate generalizations of the
approach to non-numerical data types and strategies to explore the
input (or output) space to solve different problems in Software
Engineering (\eg{}, test input generation and test
selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
paper explores diversity of sources of test cases and diversity of
engines to test and find bugs. We remain to investigate the diversity
of test cases themselves. In principle, that could help reduce the
number of alarms to inspect, for example.

>>>>

%% It automates test generation in scenarios where multiple
%% implementations of a system exist. DT leverages diversity across
%% system's implementations to detect anomalous behavior.
\emph{Related Ideas.}~The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. In contrast
to prior work on this topic, this paper explores diversity of
implementations and diversity of sources of test cases as opposed to
diversity of the test cases themselves. Section~\ref{sec:related:diversity-testing}
elaborates related work on this topic. Differential
Testing~\cite{Brumley-etal-ss07} (DT) has been applied in a variety of
contexts to find
bugs~\cite{Yang-etal-pldi11,Chen-etal-fse2015,Argyros-etla-ccs16,Chen-etal-pldi16,petsios-etal-sp2017,SivakornAPKJ17,Zhang:2017:ATD:3097368.3097448}.
It has shown to be specially practical in scenarios where the
observation of difference gives a strong signal of a real problem. For
example, Mozilla runs JS files against different configurations of a
given build of their \smonkey\ engine (\eg{}, trying to enable or not
eager JIT compilation\footnote{These files are created with the
  grammar-based fuzzer jsfunfuzz~\cite{jsfunfuzz}. Look for option
  ``compare\_jit'' from funfuzz.}). A positive aspect of the approach
is that it can be fully automated---as only one engine is used, the
outcomes of the test in both configurations are expected to be
identical. The Mozilla team uses this approach since 2002; they have
been able to find over 270 bugs since
then~\cite{jsfunfuzz-at-mozilla}, including security
bugs. Cross-engine differential testing, in contrast, has not been
widely popularized. One possible reason is that it is still not
practical to fully automate the technique. In contrast to other
applications of differential testing, a number of legitimate reasons
exist, other than a bug, for a test execution to manifest discrepancy
(see Tables~\ref{fig:piecharts-transplantation} and
~\ref{tab:false-positives}). To sum, variations of these ideas have
been explored before in different contexts.  The goal of the paper is
to assess the ability of the techniques aforementioned in finding bugs
on \javascript\ engines.

@@

\sloppy \emph{Results.}~We considered the following engines--\chakra{}
(Microsoft), JavaScriptCore (Apple), \veight{} (Google), and
\smonkey{} (Mozilla). Figure~\ref{fig:summary} shows the breakdown of
bug reports per engine (\ref{fig:stacked-engine}) and per technique
(\ref{fig:stacked-technique}). Each stacked bar breaks down the bugs
per status (\eg{}, ``1-New''). The prefix number indicates the
ordering that status labels are assigned. Note that several of these
reports have the label ``3-Fixed'', indicating that bug fixes have
been incorporated into the code already. Note that most of these bugs
affected two engines--\chakra{} and JavaScriptCore (\jsc{}).  We
reported \noBugsBugsReportedGoogle{} bugs in \veight{}
(\noBugsBugsConfirmedGoogle{} confirmed) and none in \smonkey{}.
Furthermore, our results show that both techniques revealed several
bugs, most of which confirmed by developers. Test transplantation
revealed \noBugsTransplantation{} bugs (of which,
\noBugsTransplantationConfirmed{} were confirmed and
\noBugsTransplantationFixed{} were fixed) whereas differential testing
revealed \noBugsDifferentialTesting{} bugs (of which,
\noBugsDifferentialTestingConfirmed{} were confirmed and
\noBugsDifferentialTestingFixed{} were fixed).  Overall, results
indicate that both techniques were successful at finding bugs. The
number of bug reports were similar, if we consider only those
confirmed or fixed. Most bugs we found are of moderate severity.

%% Considering cost per bug found, we found that test
%% transplantation, compared to differential testing, demanded less
%% effort from the developers who inspected the alarms.

@@

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:false-positives}Distribution of False (FP)
    and True Positives (TP).}
  \begin{tabular}{ccrr}
    \toprule
    & & \radamsa\ & \quickfuzz\ \\
    \midrule
    \multirow{4}{*}{FP} & Undefined Behavior & 42 & 16 \\ % 26 & 9 
    & Timeout/OME & 30 & 15 \\ % 28 & 13
    & * Invalid Input & 46 & 55 \\ % 39 & 48
    & * Error Message Mismatch & 41 & 12 \\ % 41 & 12
    \midrule
    \multirow{2}{*}{TP} & Duplicate & 36 & 28\\ % 34 & 28
    & Bug & 15 & 7\\
    \bottomrule     
  \end{tabular}
\end{table}

@@

\subsection{\label{sec:related:diversity-testing}Diversity in Testing}
The idea of test set diversity dates back to the
eighties~\cite{white-cohen-tse1980, ostrand-balcer-1988}. The
assumption behind test set diversity is that faults often spread
contiguously in the input domain. Consequently, it should be
beneficial to partition the input domain and explore it more evenly as
to find bugs faster. Later in the nineties, Chen and
Yu~\cite{chen-yu-tse1996} analyzed numerical software and confirmed
the continuity assumption. They found that faults, most often, manifest
themselves in regular patterns across the input
domain~\cite{Chen:2010:ART:1663656.1663914,7515474}.  Such
observations led researchers to investigate generalizations of the
approach to non-numerical data types and strategies to explore the
input (or output) space to solve different problems in Software
Engineering (\eg{}, test input generation and test
selection)~\cite{mayer-ase2005,bueno-etal-ase2007,ciupa-etal-icse08,alshahwan-harman-icse2012,alshahwan-harman-issta2014,7515474}. This
paper explores diversity of sources of test cases and diversity of
engines to test and find bugs. We remain to investigate the diversity
of test cases themselves. In principle, that could help reduce the
number of alarms to inspect, for example.
